Correlation tests

### 2025-03-20 analysis/manuscript.qmd
Report spearman

In terms of article output (see Figure \ref{fig-uptake_country}A), a strong correlation was observed across the data sources.
Between 2019 and 2023, China was the most productive country, followed by the United States and, by a certain margin, India, the United Kingdom, and Germany. 
Analysis of authorship roles revealed minimal variation, indicating that first and corresponding authors were typically from the same country.

When examining the percentage of open access articles in hybrid journals (see Figure \ref{fig-uptake_country}B), a different pattern emerged.
Authors affiliated with institutions from medium-sized European countries, such as Sweden, the Netherlands, Finland, and Hungary, provided a large proportion of their articles in open access. 
Germany and the United Kingdom also had approximately 50% of their output available as open access.
In contrast, non-OECD countries showed notably lower adoption of hybrid open access, with South Africa being the only BRICS member well-represented in the data.
The United States also demonstrated a relatively low proportion of open access articles.
These findings were consistent across all databases.
However, France was better represented in Web of Science, likely due to its agreement with Elsevier starting in 2019, which allowed delayed open access under the publisher’s user license [@Rabesandratana_2019]. 
This license was not classified as hybrid open access in Scopus or hoaddata.

@@

>>>>

In terms of article output by country (see Figure \ref{fig-uptake_country}A), strong positive correlation was observed across the data sources and author roles (Spearman rank correlation $\rho > .9$, $p < 0.001$).
Between 2019 and 2023, China was the most productive country, followed by the United States and, by a certain margin, India, the United Kingdom, and Germany. 
Analysis of authorship roles revealed minimal variation, indicating that first and corresponding authors were typically from the same country.

When examining the percentage of open access articles in hybrid journals (see Figure \ref{fig-uptake_country}B), a different pattern emerged.
Authors affiliated with institutions from medium-sized European countries, such as Sweden, the Netherlands, Finland, and Hungary, provided a large proportion of their articles in open access.
Germany and the United Kingdom also had approximately 40% of their output available as open access.
In contrast, non-OECD countries showed notably lower adoption of hybrid open access, with South Africa being the only BRICS member well-represented in the data.
The United States also demonstrated a relatively low proportion of open access articles.
These findings were consistent across all databases.
However, France was better represented in Web of Science, likely due to its agreement with Elsevier starting in 2019, which allowed delayed open access under the publisher’s user license [@Rabesandratana_2019]. 
This license was not classified as hybrid open access in Scopus or hoaddata.
In all cases, Spearman rank correlations were $\rho > .9$, $p < 0.001$, showing a high level of correlations between the databases and authorship roles considered.

@@

In all cases, strong positive correlations were observed using Spearman's rank correlation: 
$\rho > .9$, $p < 0.001$ between data sources and authorship roles, when considering countries with an minimum of 1,000 open access articles enabled by transformative agreements between 2019 and 2023. 
When this limitation was removed, the correlation remained strong but slightly lower ($\rho > .85$, $p < 0.001$).
This difference may signal countries where only a few institutions had transformative agreements in place, as opposed to those participating in national consortia with broader participation.

### 2025-03-20 analysis/manuscript.tex
Report spearman

In terms of article output (see Figure \ref{fig-uptake_country}A), a
strong correlation was observed across the data sources. Between 2019
and 2023, China was the most productive country, followed by the United
States and, by a certain margin, India, the United Kingdom, and Germany.
Analysis of authorship roles revealed minimal variation, indicating that
first and corresponding authors were typically from the same country.

When examining the percentage of open access articles in hybrid journals
(see Figure \ref{fig-uptake_country}B), a different pattern emerged.
Authors affiliated with institutions from medium-sized European
countries, such as Sweden, the Netherlands, Finland, and Hungary,
provided a large proportion of their articles in open access. Germany
and the United Kingdom also had approximately 50\% of their output
available as open access. In contrast, non-OECD countries showed notably
lower adoption of hybrid open access, with South Africa being the only
BRICS member well-represented in the data. The United States also
demonstrated a relatively low proportion of open access articles. These
findings were consistent across all databases. However, France was
better represented in Web of Science, likely due to its agreement with
Elsevier starting in 2019, which allowed delayed open access under the
publisher's user license (Rabesandratana, 2019). This license was not
classified as hybrid open access in Scopus or hoaddata.

@@

>>>>

In terms of article output by country (see Figure
\ref{fig-uptake_country}A), strong positive correlation was observed
across the data sources and author roles (Spearman rank correlation
\(\rho > .9\), \(p < 0.001\)). Between 2019 and 2023, China was the most
productive country, followed by the United States and, by a certain
margin, India, the United Kingdom, and Germany. Analysis of authorship
roles revealed minimal variation, indicating that first and
corresponding authors were typically from the same country.

When examining the percentage of open access articles in hybrid journals
(see Figure \ref{fig-uptake_country}B), a different pattern emerged.
Authors affiliated with institutions from medium-sized European
countries, such as Sweden, the Netherlands, Finland, and Hungary,
provided a large proportion of their articles in open access. Germany
and the United Kingdom also had approximately 40\% of their output
available as open access. In contrast, non-OECD countries showed notably
lower adoption of hybrid open access, with South Africa being the only
BRICS member well-represented in the data. The United States also
demonstrated a relatively low proportion of open access articles. These
findings were consistent across all databases. However, France was
better represented in Web of Science, likely due to its agreement with
Elsevier starting in 2019, which allowed delayed open access under the
publisher's user license (Rabesandratana, 2019). This license was not
classified as hybrid open access in Scopus or hoaddata. In all cases,
Spearman rank correlations were \(\rho > .9\), \(p < 0.001\), showing a
high level of correlations between the databases and authorship roles
considered.

@@

In all cases, strong positive correlations were observed using
Spearman's rank correlation: \(\rho > .9\), \(p < 0.001\) between data
sources and authorship roles, when considering countries with an minimum
of 1,000 open access articles enabled by transformative agreements
between 2019 and 2023. When this limitation was removed, the correlation
remained strong but slightly lower (\(\rho > .85\), \(p < 0.001\)). This
difference may signal countries where only a few institutions had
transformative agreements in place, as opposed to those participating in
national consortia with broader participation.
